A comps-based approach for interpreting tree-based predictions

### 2025-05-19 articles/arxiv/paper.tex
very minor wording change

Average QBR per season is the response variable describing the success of quarterback prospects. Because of the date ranges of the data, we do not calculate this perfectly for all of the quarterbacks in our dataset. On one end of the extremes, quarterbacks who finished their college careers in 2001 may have appeared in the NFL but only before 2006. These quarterbacks have a QBR of zero in our dataset. On the other end of the extremes, quarterbacks who finished their college careers in 2023 and have not yet appeared in the NFL may yet do so. These quarterbacks, too, have a QBR of zero in our dataset. This is a limitation of the data.

>>>>

Average QBR per season is the response variable describing the success of quarterback prospects. Because of the date ranges of the data, we do not calculate this perfectly for all of the quarterbacks in our dataset. On one extremes, quarterbacks who finished their college careers in 2001 may have appeared in the NFL but only before 2006. These quarterbacks have a QBR of zero in our dataset. On the other extreme, quarterbacks who finished their college careers in 2023 and have not yet appeared in the NFL may yet do so. These quarterbacks, too, have a QBR of zero in our dataset. This is a limitation of the data.
